FHJ: A Formal Model for Hierarchical Dispatching and Overriding

### 2017-10-17 NewVersion/sections/Formalization.tex
typos, grammar, S1 to S4

\section{Formalization}~\label{sec:formalization}
In this section, we present a formal model called \MIM{} (\emph{\textbf{F}eatherweight \textbf{H}ierarchical \textbf{J}ava}), following similar style of 
Featherweight Java~\cite{Igarashi01FJ}. \MIM{} is a minimal core calculus that formalizes the core concept of hierarchical dispatching and overriding. The syntax, typing rules and small-step semantics are presented.

% \vspace{-2ex}
\subsection{Syntax}
The abstract syntax of \MIM{} interface declarations, method declarations, and expressions is given at Figure~\ref{fig:syntax}. The multiple
inheritance feature of \MIM{} is inspired by Java 8 interfaces, which supports
method implementations via default methods. This feature is 
closely related to \emph{traits}. To demonstrate how
unintentional method conflicts are untangled in \MIM{}, we only focus on a small subset of the interface model. For example, all methods declared
in an interface are either default methods or abstract methods. Default methods provide default implementations for methods. Abstract methods do not
have a method body. Abstract methods can be overridden with future implementations.

\paragraph{Notations}
The metavariables $I, J$ range over interface names; $x$ ranges over variables; $m$ ranges over method names; $e$ ranges over expressions; and $M$ ranges over method declarations. Following Featherweight Java, we assume that the set of variables includes the special variable \kwthis, which cannot be used as the name of an argument to a method. We use the same
conventions as FJ; we write $\overline{I}$ as shorthand for a possibly empty sequence $I_1, ..., I_n$, which may be indexed by $I_i$; and write $\overline{M}$ as shorthand for $M_1 .. M_n$ (with no commas). We also abbreviate operations on pairs of sequences in the obvious way, writing $\overline{I} \; \overline{x}$ for $I_1 \; x_1, ..., I_n \; x_n$, where $n$ is the length of $\overline{I}$ and $\overline{x}$.

@@

The second condition of \textsc{(T-Intf)} is more complex, and is the key to type soundness. Unlike C++ which rejects on ambiguous calls,
\MIM{} rejects on the definition of interfaces when they form a diamond. Consider the case when the second condition is broken: $\mbody(m, J, J)$
is defined but $\mbody(m, I, J)$ is undefined for some $J$ and $m$. This indicates that $m$ is available and unambiguous from the perspective of $J$,
but is ambiguous to $I$ on branch $J$. It means that there are multiple overriding paths of $m$ from $J$ to $I$, which forms a diamond. Hence rejecting
that case meets our expectation. Below is an example (Figure~\ref{fig:examplesmbody} (e)) that illustrates the reason why this condition is needed:
\bruno{what is the purpose of this example:
  state-it upfront please. Is this example meant to ilustrate T-Inf?
  Then it's better to have the example together with the text
  explaining T-inf.} \yanlin{revised.please check whether you're happy with it.}
\vspace{3pt}\begin{lstlisting}
interface T                 { T m() override T { return new T(); } }
interface A extends T       { T m() override T { return new A(); } }
interface B extends T       { T m() override T { return new B(); } }
interface C extends A, B {}

@@

\paragraph{Congruence Rules} \textsc{(C-Receiver)}, \textsc{(C-Args)} and \textsc{(C-FReduce)} are natural congruence rules
on receivers, arguments and cast-expressions, respectively. \textsc{(C-StaticType)} automatically adds an annotation $I$ to the new
object $\new{I}$. \textsc{(C-AnnoReduce)} merges nested upcasts into a single upcast with the outermost type.

>>>>

\section{Formalization}~\label{sec:formalization}
In this section, we present a formal model called \MIM{} (\emph{\textbf{F}eatherweight \textbf{H}ierarchical \textbf{J}ava}), following the similar style of 
Featherweight Java~\cite{Igarashi01FJ}. \MIM{} is a minimal core calculus that formalizes the core concept of hierarchical dispatching and overriding. The syntax, typing rules and small-step semantics are presented.

% \vspace{-2ex}
\subsection{Syntax}
The abstract syntax of \MIM{} interface declarations, method declarations, and expressions is given in Figure~\ref{fig:syntax}. The multiple
inheritance feature of \MIM{} is inspired by Java 8 interfaces, which supports
method implementations via default methods. This feature is 
closely related to \emph{traits}. To demonstrate how
unintentional method conflicts are untangled in \MIM{}, we only focus on a small subset of the interface model. For example, all methods declared
in an interface are either default methods or abstract methods. Default methods provide default implementations for methods. Abstract methods do not
have a method body. Abstract methods can be overridden with future implementations.

\paragraph{Notations}
The metavariables $I, J$ range over interface names; $x$ ranges over variables; $m$ ranges over method names; $e$ ranges over expressions; and $M$ ranges over method declarations. Following Featherweight Java, we assume that the set of variables includes the special variable \kwthis, which cannot be used as the name of an argument to a method. We use the same
conventions as FJ; we write $\overline{I}$ as shorthand for a possibly empty sequence $I_1, ..., I_n$, which may be indexed by $I_i$; and write $\overline{M}$ as shorthand for $M_1 .. M_n$ (with no commas). We also abbreviate operations on pairs of sequences in an obvious way, writing $\overline{I} \; \overline{x}$ for $I_1 \; x_1, ..., I_n \; x_n$, where $n$ is the length of $\overline{I}$ and $\overline{x}$.

@@

The second condition of \textsc{(T-Intf)} is more complex and is the key to type soundness. Unlike C++ which rejects on ambiguous calls,
\MIM{} rejects on the definition of interfaces when they form a diamond. Consider the case when the second condition is broken: $\mbody(m, J, J)$
is defined but $\mbody(m, I, J)$ is undefined for some $J$ and $m$. This indicates that $m$ is available and unambiguous from the perspective of $J$,
but is ambiguous to $I$ on branch $J$. It means that there are multiple overriding paths of $m$ from $J$ to $I$, which forms a diamond. Hence rejecting
that case meets our expectation. Below is an example (Figure~\ref{fig:examplesmbody} (e)) that illustrates the reason why this condition is needed:
\bruno{what is the purpose of this example:
  state-it upfront please. Is this example meant to ilustrate T-Inf?
  Then it's better to have the example together with the text
  explaining T-inf.} \yanlin{revised.please check whether you're happy with it.}
\vspace{3pt}\begin{lstlisting}
interface T                 { T m() override T { return new T(); } }
interface A extends T       { T m() override T { return new A(); } }
interface B extends T       { T m() override T { return new B(); } }
interface C extends A, B {}

@@

\paragraph{Congruence Rules} \textsc{(C-Receiver)}, \textsc{(C-Args)} and \textsc{(C-FReduce)} are natural congruence rules
on receivers, arguments, and cast-expressions, respectively. \textsc{(C-StaticType)} automatically adds an annotation $I$ to the new
object $\new{I}$. \textsc{(C-AnnoReduce)} merges nested upcasts into a single upcast with the outermost type.

### 2017-10-17 NewVersion/sections/Introduction.tex
typos, grammar, S1 to S4

In contrast to diamond inheritance, a second case of ambiguity
is \textit{unintentional method conflicts}~\cite{scharli03traits}. It is that the conflicting 
methods do not actually refer to the same feature. 
In a nominal system, methods can be designed for different
functionality, but happen to have the same names (and signatures).
A simple example of this situation is two \lstinline{draw} methods that
are inherited from a deck of cards and a drawable widget. 
In such context, the two \lstinline{draw} methods have very different meanings, 
but they happen to share the same name.
%%This issue was proposed by the trait paper, so-called
When inheritance is used to compose these methods, a compilation 
error happens due to conflicts. However, unlike the diamond problem,
the conflicting methods have very different meanings and do not share a
common parent. We call such a case \textit{triangle inheritance}, in
analogy to diamond inheritance.

@@

C++ and C\# do allow for two
unintentionally conflicting methods to coexist in a class. C\# allows
this by interface multiple inheritance and explicit method
implementations. But since C\# is a single inheritance language, 
it is only possible to \emph{implement} multiple interfaces (but not
multiple classes). %We will have more detailed discussion on this in Section~\ref{sec:relatedwork}.
C++ accepts triangle inheritance and
resolves the ambiguity by specifying the expected path by
\emph{upcasts}. However
neither the C\# or C++ approaches allow
such conflicting methods to be further overridden. 
% However, C++ has
% limited support for virtual methods with unintentional conflicts, and
% it will often throw errors when composing them. This is again
% unsatisfactory because virtual methods are pervasive in OOP and used 
% for code reuse and extensibility. A problem with the C++ approach is
% that programmers can only use either static or dynamic dispatching separately, but dealing
% with unintentional method conflicts seems to require a combination of
% both. 
Some other workarounds or approaches include delegation and
renaming/exclusion in the trait model. However renaming/exclusion 
can break the subtyping relation between a subclass and its parent.
This is not adequate for the class model commonly used in mainstream 
OOP languages, where the subclass is always expected to be a subtype 
of the parent class.

@@

\textit{Hierarchical overriding} is a novel language
mechanism that allows method overriding to be applied
only to one branch of the class hierarchy. Hierarchical overriding 
adds expressive power that is not available in languages such as 
C++ or C\#. Hierarchical overriding allows overriding to work 
for classes with multiple (conflicting) methods sharing the 
same names and signatures. An example is presented in 
Figure~\ref{fig:main}. In this example there are 4 classes/interfaces.
Two classes model a deck of cards (\lstinline|Deck|) and a class for
drawable widgets (\lstinline|Drawable|). 
The class \lstinline|SafeDeck| adds functionality to check whether the
deck is empty and to prevent drawing a card from an empty deck. 
The interesting class is \lstinline|DrawableSafeDeck|, which inherits 
from both \lstinline|SafeDeck| and \lstinline|Drawable|. Hierarchical
overriding is used in \lstinline|DrawableSafeDeck| to keep two separate \lstinline|draw|
methods for each parent, but overriding \emph{only} the \lstinline|draw|
method coming from \lstinline|Drawable|, in order to draw a widget
with a deck of cards. Note that hierarchical overriding is denoted in the UML
diagram with the notation
\lstinline|draw()|$\shneg$\lstinline|Drawable|. It expresses that the \lstinline|draw| method from \lstinline|Drawable|
is overridden. Although in this example only one of the
\lstinline|draw| methods is overridden (and the other is simply inherited), hierarchical overriding
supports multiple conflicting methods to be independently overridden as well.

To present hierarchical overriding and dispatching, we introduce a
formalized model \MIM{} in Section~\ref{sec:formalization} based on
Featherweight Java~\cite{Igarashi01FJ}, together with theorems and
proofs for type soundness. 
In summary, our contributions are:
\begin{itemize}
	\item \textbf{Formalization of a hierarchical dispatching algorithm} that integrates both the static type and dynamic type for method dispatch, and hence
	ensures unambiguity as well as extensibility in the presence
        of unintentional method conflicts.
	\item \textbf{Hierarchical overriding:} a novel notion that allows
          methods to override individual branches of the class hierarchy.
	\item \textbf{\name:} a formalized model based on
          Featherweight Java, supporting the above features. 
          We provide the static and dynamic semantics, and prove the
          type soundness of the model.
	\item \textbf{Prototype implementation\footnote{Available in
              supplementary material attached to the submission.}:} a
          simple implementation of \MIM{} interpreter in Scala.
\end{itemize}

>>>>

In contrast to diamond inheritance, the second case of ambiguity
is \textit{unintentional method conflicts}~\cite{scharli03traits}. It is that the conflicting 
methods do not actually refer to the same feature. 
In a nominal system, methods can be designed for different
functionality, but happen to have the same names (and signatures).
A simple example of this situation is two \lstinline{draw} methods that
are inherited from a deck of cards and a drawable widget. 
In such context, the two \lstinline{draw} methods have very different meanings, 
but they happen to share the same name.
%%This issue was proposed by the trait paper, so-called
When inheritance is used to compose these methods, a compilation 
error happens due to conflicts. However, unlike the diamond problem,
the conflicting methods have very different meanings and do not share a
common parent. We call such a case \textit{triangle inheritance}, in
analogy to diamond inheritance.

@@

C++ and C\# do allow for two
unintentionally conflicting methods to coexist in a class. C\# allows
this by interface multiple inheritance and explicit method
implementations. But since C\# is a single inheritance language, 
it is only possible to \emph{implement} multiple interfaces (but not
multiple classes). %We will have more detailed discussion on this in Section~\ref{sec:relatedwork}.
C++ accepts triangle inheritance and
resolves the ambiguity by specifying the expected path by
\emph{upcasts}. However, neither the C\# or C++ approaches allow
such conflicting methods to be further overridden. 
% However, C++ has
% limited support for virtual methods with unintentional conflicts, and
% it will often throw errors when composing them. This is again
% unsatisfactory because virtual methods are pervasive in OOP and used 
% for code reuse and extensibility. A problem with the C++ approach is
% that programmers can only use either static or dynamic dispatching separately, but dealing
% with unintentional method conflicts seems to require a combination of
% both. 
Some other workarounds or approaches include delegation and
renaming/exclusion in the trait model. However renaming/exclusion 
can break the subtyping relation between a subclass and its parent.
This is not adequate for the class model commonly used in mainstream 
OOP languages, where the subclass is always expected to be a subtype 
of the parent class.

@@

\textit{Hierarchical overriding} is a novel language
mechanism that allows method overriding to be applied
only to one branch of the class hierarchy. Hierarchical overriding 
adds expressive power that is not available in languages such as 
C++ or C\#. Hierarchical overriding allows overriding to work 
for classes with multiple (conflicting) methods sharing the 
same names and signatures. An example is presented in 
Figure~\ref{fig:main}. In this example, there are 4 classes/interfaces.
Two classes model a deck of cards (\lstinline|Deck|) and a class for
drawable widgets (\lstinline|Drawable|). 
The class \lstinline|SafeDeck| adds functionality to check whether the
deck is empty and to prevent drawing a card from an empty deck. 
The interesting class is \lstinline|DrawableSafeDeck|, which inherits 
from both \lstinline|SafeDeck| and \lstinline|Drawable|. Hierarchical
overriding is used in \lstinline|DrawableSafeDeck| to keep two separate \lstinline|draw|
methods for each parent, but overriding \emph{only} the \lstinline|draw|
method coming from \lstinline|Drawable|, in order to draw a widget
with a deck of cards. Note that hierarchical overriding is denoted in the UML
diagram with the notation
\lstinline|draw()|$\shneg$\lstinline|Drawable|. It expresses that the \lstinline|draw| method from \lstinline|Drawable|
is overridden. Although in this example only one of the
\lstinline|draw| methods is overridden (and the other is simply inherited), hierarchical overriding
supports multiple conflicting methods to be independently overridden as well.

To present hierarchical overriding and dispatching, we introduce a
formalized model \MIM{} in Section~\ref{sec:formalization} based on
Featherweight Java~\cite{Igarashi01FJ}, together with theorems and
proofs for type soundness. 
In summary, our contributions are:
\begin{itemize}
	\item \textbf{Formalization of a hierarchical dispatching algorithm} that integrates both the static type and dynamic type for method dispatch, and hence
	ensures unambiguity as well as extensibility in the presence
        of unintentional method conflicts.
	\item \textbf{Hierarchical overriding:} a novel notion that allows
          methods to override individual branches of the class hierarchy.
	\item \textbf{\name:} a formalized model based on
          Featherweight Java, supporting the above features. 
          We provide the static and dynamic semantics and prove the
          type soundness of the model.
	\item \textbf{Prototype implementation\footnote{Available in
              supplementary material attached to the submission.}:} a
          simple implementation of \MIM{} interpreter in Scala.
\end{itemize}

### 2017-10-17 NewVersion/sections/Overview.tex
typos, grammar, S1 to S4

\section{A Running Example: Drawable Deck}~\label{sec:overview}
This section illustrates the problem of unintentional method conflicts,
together with the features of our model on addressing this issue, by
a simple running example. In the following text we will introduce three
problems one by one, and have a discussion on possible workarounds and
our solutions.
Problems 1 and 2 are related to hierarchical dispatching, and in 
C++ it is possible to have similar solutions as ours to both
problems. Hence it is important to emphasize that, with respect to
hierarchical dispatching, our contribution is not a novel
mechanism. Instead, 
inspired by the C++ solution, our contribution is formalizing a minimal calculus
of this feature together with a proof of type soundness. However, for the final problem, there is no satisfactory approach
in existing languages, thus we propose a new feature (hierarchical
overriding) with the corresponding formalization of that feature.

@@

interface Drawable {
  void draw() { // draws something on the screen
    JFrame frame = new JFrame();
    frame.setVisible(true);
  }
}
\end{lstlisting}\vspace{3pt}
In \lstinline|Deck|,
\lstinline|draw| uses \lstinline|println|, which is a
library function. 
The two \lstinline|draw| methods can have different return types, but for simplicity
they both return \lstinline|void| here. Note that, similarly to
Featherweight Java~\cite{Igarashi01FJ}, \lstinline|void| is
unsupported in our formalization. We could have also defined an interface called \lstinline|Void|
and return an object of that type instead. To be concise, we use \lstinline|void| in this code.
For \lstinline|Drawable| the \lstinline|draw|
creates a blank canvas by \lstinline|JFrame| and set the visibility to \lstinline|true|.

@@

Now, supppose that a programmer is designing a
card game with a GUI. He may want to draw a deck on the screen, so he first defines a drawable
deck using multiple inheritance:

@@

\paragraph{Problem and Possible Workarounds:} The essential problem is
how to resolve unintentional method conflicts and invoke the
conflicting methods separately without ambiguity. To this problem, there are several other workarounds
that come to our mind. We briefly discuss those potential fixes and
workarounds next:
\begin{itemize}
  \item \textit{I. Delegation.} As an alternative to multiple inheritance,
  delegation can be used by introducing two fields (or field methods) with
  \lstinline|Drawable| type and \lstinline|Deck| type,
  respectively. This avoids method conflicts. Nevertheless, it is known
  that using delegation makes it hard to correctly maintain
  self-references in an extensible system and also
  introduces a lot of boilerplate code.
  \item \textit{II. Refactor Drawable and/or Deck to rename the methods.} If
  the source code for \lstinline|Drawable| or \lstinline|Deck| is available
  then it may be possible to rename one of the \lstinline|draw|
  methods. However this approach is non-modular, as it requires 
  modifying existing code, and may not be possible if code is unavailable.
  \item \textit{III. Method exclusion/renaming in traits.} Some trait models
  support method exclusion/renaming. Those features
   can eliminate conflicts, although most
  programming languages do not support them. In a traditional OO system,
  they can break the subtyping relationship. Moreover, in
  contrast with exclusion, renaming can indeed preserve both conflicting
  behaviours. However, it is cumbersome in practice, as introducing new
  names can affect other code blocks.
\end{itemize}

@@

\paragraph{\MIM{}'s solution:} To solve this problem it is important to preserve both conflicting methods
during inheritance instead of merging them into a single
method. Therefore \MIM{} accepts the definition of \lstinline|DrawableDeck|. To disambiguite method calls
we can use \emph{up-casts} in \MIM{}, so as to specify the ``branch'' in the
inheritance hierarchy that should be called. The following code
illustrates the use of up-casts for disambiguation:

@@

// main program
((Deck) new DrawableDeck()).draw()  // calls Deck.draw
// (new DrawableDeck()).draw()        // this call is ambiguous and rejected
\end{lstlisting}\vspace{3pt}
In our language, the main program is merely an expression. The above cast indicates
that we expect to invoke the \lstinline|draw| from branch
\lstinline|Deck|. Similarly we could have used an upcast to \lstinline|Drawable|
to call the \lstinline|draw| method from \lstinline|Drawable|.
Without the cast the call would be ambiguous, and
\MIM{}'s type system would reject that call.

@@

\subsection{Problem 3: Overriding on Individual Branches}\label{subsec:partialoverrides}
Method overriding is common in Object-Oriented Programming. 
With diamond inheritance where conflicting methods are intended to have 
the same semantics, method overriding is not a problem. If conflicting
methods arize from multiple parents, we can override all those methods 
in a single unified (or merged) method in the subclass. Therefore
further overriding is simple, because there is only one method that
can be overriden.

With unintentional method conflicts, however, the situation is more
complicated because different, separate, conflicting methods can coexist
in one class. Ideally we would like to support overriding for those
methods too, in exactly the same way that overriding is available for 
other (non-conflicting) methods. However we need to be able to
override the individual conflicting methods, rather than overriding all
conflicting methods into a single merged one. We illustrate the
problem and the need for a more refined overrding mechanism with 
an example.

>>>>

\section{A Running Example: Drawable Deck}~\label{sec:overview}
This section illustrates the problem of unintentional method conflicts,
together with the features of our model on addressing this issue, by
a simple running example. In the following text we will introduce three
problems one by one and have a discussion on possible workarounds and
our solutions.
Problems 1 and 2 are related to hierarchical dispatching, and in 
C++ it is possible to have similar solutions as ours to both
problems. Hence it is important to emphasize that, with respect to
hierarchical dispatching, our contribution is not a novel
mechanism. Instead, 
inspired by the C++ solution, our contribution is formalizing a minimal calculus
of this feature together with a proof of type soundness. However, for the final problem, there is no satisfactory approach
in existing languages, thus we propose a new feature (hierarchical
overriding) with the corresponding formalization of that feature.

@@

interface Drawable {
  void draw() { // draws something on the screen
    JFrame frame = new JFrame();
    frame.setVisible(true);
  }
}
\end{lstlisting}\vspace{3pt}
In \lstinline|Deck|,
\lstinline|draw| uses \lstinline|println|, which is a
library function. 
The two \lstinline|draw| methods can have different return types, but for simplicity, 
they both return \lstinline|void| here. Note that, similarly to
Featherweight Java~\cite{Igarashi01FJ}, \lstinline|void| is
unsupported in our formalization. We could have also defined an interface called \lstinline|Void|
and return an object of that type instead. To be concise, we use \lstinline|void| in this code.
For \lstinline|Drawable| the \lstinline|draw|
creates a blank canvas by \lstinline|JFrame| and set the visibility to \lstinline|true|.

@@

Now, suppose that a programmer is designing a
card game with a GUI. He may want to draw a deck on the screen, so he first defines a drawable
deck using multiple inheritance:

@@

\paragraph{Problem and Possible Workarounds:} The essential problem is
how to resolve unintentional method conflicts and invoke the
conflicting methods separately without ambiguity. To this problem, there are several other workarounds
that come to our mind. We briefly discuss those potential fixes and
workarounds next:
\begin{itemize}
  \item \textit{I. Delegation.} As an alternative to multiple inheritance,
  delegation can be used by introducing two fields (or field methods) with
  \lstinline|Drawable| type and \lstinline|Deck| type,
  respectively. This avoids method conflicts. Nevertheless, it is known
  that using delegation makes it hard to correctly maintain
  self-references in an extensible system and also
  introduces a lot of boilerplate code.
  \item \textit{II. Refactor Drawable and/or Deck to rename the methods.} If
  the source code for \lstinline|Drawable| or \lstinline|Deck| is available
  then it may be possible to rename one of the \lstinline|draw|
  methods. However this approach is non-modular, as it requires 
  modifying existing code, and may not be possible if the code is unavailable.
  \item \textit{III. Method exclusion/renaming in traits.} Some trait models
  support method exclusion/renaming. Those features
   can eliminate conflicts, although most
  programming languages do not support them. In a traditional OO system,
  they can break the subtyping relationship. Moreover, in
  contrast with exclusion, renaming can indeed preserve both conflicting
  behaviours. However, it is cumbersome in practice, as introducing new
  names can affect other code blocks.
\end{itemize}

@@

\paragraph{\MIM{}'s solution:} To solve this problem it is important to preserve both conflicting methods
during inheritance instead of merging them into a single
method. Therefore \MIM{} accepts the definition of \lstinline|DrawableDeck|. To disambiguate method calls, 
we can use \emph{up-casts} in \MIM{}, so as to specify the ``branch'' in the
inheritance hierarchy that should be called. The following code
illustrates the use of up-casts for disambiguation:

@@

// main program
((Deck) new DrawableDeck()).draw()  // calls Deck.draw
// (new DrawableDeck()).draw()        // this call is ambiguous and rejected
\end{lstlisting}\vspace{3pt}
In our language, the main program is merely an expression. The above cast indicates
that we expect to invoke the \lstinline|draw| from branch
\lstinline|Deck|. Similarly we could have used an upcast to \lstinline|Drawable|
to call the \lstinline|draw| method from \lstinline|Drawable|.
Without the cast, the call would be ambiguous and
\MIM{}'s type system would reject that call.

@@

\subsection{Problem 3: Overriding on Individual Branches}\label{subsec:partialoverrides}
Method overriding is common in Object-Oriented Programming. 
With diamond inheritance where conflicting methods are intended to have 
the same semantics, method overriding is not a problem. If conflicting
methods arise from multiple parents, we can override all those methods 
in a single unified (or merged) method in the subclass. Therefore
further overriding is simple, because there is only one method that
can be overridden.

With unintentional method conflicts, however, the situation is more
complicated because different, separate, conflicting methods can coexist
in one class. Ideally we would like to support overriding for those
methods too, in exactly the same way that overriding is available for 
other (non-conflicting) methods. However we need to be able to
override the individual conflicting methods, rather than overriding all
conflicting methods into a single merged one. We illustrate the
problem and the need for a more refined overriding mechanism with 
an example.
